---
title: "Lab 01 - Hello R"
author: "Andy Ng"
date: "5/23/2023"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.

### Exercise 2

dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

dino_data %>%
  summarize(r = cor(x, y))
#> # A tibble: 1 × 1
#>         r
#>     <dbl>
#> 1 -0.0645

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
#> # A tibble:
#> #   13 × 2
#>    dataset   
#>    <chr>     
#>  1 away      
#>  2 bullseye  
#>  3 circle    
#>  4 dino      
#>  5 dots      
#>  6 h_lines   
#>  7 high_lines
#>  8 slant_down
#>  9 slant_up  
#> 10 star      
#> 11 v_lines   
#> 12 wide_lines
#> 13 x_shape   
#> # ℹ 1 more
#> #   variable:
#> #   n <int>

### Exercise 3

```{r plot-star, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```



### Exercise 4



```{r plot-circle, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.




